---
title: "Corolla Pricing Model"
format: html
editor: visual
---

### Required Installations

After exporting this document, please remember to ensure the following packages are installed on your computer. Then you erase this content from your document/assignment.

-   rmarkdown

-   tidyverse

-   rpart, rpart.plot

-   caret

-   gamlr

------------------------------------------------------------------------

```{r}
#| message: false
library(tidyverse)
library(rpart)
library(caret)
library(GGally)
```

## Read in and Prepare Data

```{r}
cars = read_csv("ToyotaCorolla.csv")
glimpse(cars)
```

```{r}
cars = cars %>%
  select(-Id, -Model, -Mfg_Month, -Cylinders)
```

Important Features

mileage (kilometers)

year/age

wear and tear

clean title

damage/condition

AWD/FWD/RWD

color

Fuel Type

```{r}
cars_fct = cars %>%
  select(-Price, -Age_08_04, -KM, -HP, -CC, -Quarterly_Tax, -Weight) %>%
  mutate_all(.funs = factor)

cars_num = cars %>%
  select(Price, Age_08_04, KM, HP, CC, Quarterly_Tax, Weight)

cars2 = bind_cols(cars_num, cars_fct)
```

```{r}
#| message: false
cars2 %>%
  keep(is.numeric) %>%
  ggpairs()
```

kitchen sink model below

```{r}
lm1 = lm(Price ~ Age_08_04 + KM,
         data = cars2)
summary(lm1)
```
